\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{sourcesanspro}

\renewcommand{\familydefault}{\sfdefault}

\hyphenpenalty=500
\exhyphenpenalty=500
\emergencystretch=2em

\titleformat{\section}{\large\bfseries}{\thesection.}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{0.5em}{}

\setlist[itemize]{noitemsep,topsep=3pt}

\begin{document}

{\LARGE \textbf{Equal Opportunity \& Non-Discrimination Statement}}

\vspace{4pt}
RePass Cloud Pty Ltd

\vspace{2pt}
Last updated: 2025-01-01

\vspace{12pt}

\section{Our Commitment}

RePass Cloud is an equal opportunity employer and contractor. We are committed to building a team where talent, curiosity, and character determine success --- not background, identity, or circumstance.

This statement applies to all employees, contractors, and third-party organisations engaged by RePass Cloud.

\section{Legislative Framework}

RePass Cloud operates in accordance with applicable Australian anti-discrimination legislation, including:

\begin{itemize}
\item \href{https://www.legislation.gov.au/C2009A00028}{Fair Work Act 2009}
\item \href{https://www.legislation.gov.au/C2004A02868}{Sex Discrimination Act 1984}
\item \href{https://www.legislation.gov.au/C2004A04426}{Disability Discrimination Act 1992}
\item \href{https://www.legislation.gov.au/C2004A01302}{Age Discrimination Act 2004}
\item \href{https://www.legislation.gov.au/C2004A00274}{Racial Discrimination Act 1975}
\end{itemize}

We do not discriminate on the basis of age, sex, gender identity, race, colour, ethnicity, national origin, religion, disability, marital status, pregnancy, political opinion, or any other attribute protected under applicable law.

\section{Scope}

This policy applies to:

\begin{itemize}
\item All stages of the hiring process --- application, screening, interview, and offer
\item All engagements --- full-time employees, part-time employees, and independent contractors
\item All geographies --- we hire locally in Australia and internationally
\item Third-party organisations --- when we award work to an external organisation, we expect that organisation to uphold equivalent equal opportunity standards for its own employees and contractors
\end{itemize}

\section{Applicants with Disabilities}

We are committed to providing reasonable accommodations to applicants with disabilities throughout the hiring process. If you require any adjustment or support during your application or interview, please let us know at the time of application. We can only provide support when we are informed, and we encourage all candidates to communicate their needs without hesitation.

\section{Criminal History}

RePass Cloud recognises that past convictions do not define a person's future. Applicants with a criminal record will be considered for all roles. Where a criminal history is directly relevant to the responsibilities of a role --- for example, a history of financial fraud for a role with fiduciary responsibility --- it will be taken into account proportionately. Where it is not relevant, it will not be considered.

We believe in second chances and in assessing candidates on the merit of who they are today.

\section{Hiring Decisions}

All hiring and engagement decisions are made on the basis of:

\begin{itemize}
\item Skills and technical capability
\item Relevant experience
\item Professional conduct
\end{itemize}

Professional conduct at RePass Cloud means how you engage with people, represent the brand, and operate with integrity --- not how you dress or what you look like.

\section{Reporting Concerns}

Any applicant, employee, or contractor who believes they have experienced discrimination during a RePass Cloud hiring or engagement process is encouraged to raise the matter via our \href{/contact/}{contact page}. All concerns will be treated seriously and handled with appropriate confidentiality.

\end{document}