\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{sourcesanspro}

\renewcommand{\familydefault}{\sfdefault}

\hyphenpenalty=10000
\exhyphenpenalty=10000
\sloppy

\titleformat{\section}{\large\bfseries}{\thesection.}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{0.5em}{}

\setlist[itemize]{noitemsep,topsep=3pt}

\begin{document}

{\LARGE \textbf{Privacy Policy}}

\vspace{4pt}
RePass Cloud Pty Ltd

\vspace{2pt}
Last updated: 2026-03-07

\vspace{12pt}

\section{Who We Are}

This Privacy Policy applies to RePass Cloud Pty Ltd ("RePass Cloud", "we", "us", or "our"). It explains how we collect, use, disclose, store, and protect personal information when you interact with our websites, products, and services (the "Services").

Our actively developed and maintained enterprise SaaS product is Cinturon360. We may also operate additional websites, brands, prototypes, or legacy products. This policy applies to all Services we operate that link to this Privacy Policy.

Legacy notice: LunaVPN is not an active RePass Cloud service. The source code has been made available as open source and it is not actively maintained or operated by us.

If you do not agree with this policy, do not use the Services.

\section{Roles: Controller and Processor}

Depending on the context, RePass Cloud may act as:

\begin{itemize}
\item Data controller (for example, for account administration, billing, and operating our websites and marketing activities).
\item Data processor / service provider (for example, when we process data on behalf of a business customer in enterprise SaaS products such as Cinturon360).
\end{itemize}

Business customers are typically the controller for customer content they upload to enterprise SaaS products.

\section{Contact Details}

RePass Cloud Pty Ltd \\
PO BOX 262 \\
Bondi Junction NSW 1355 \\
Australia

Email: \href{mailto:hello@repasscloud.com}{hello@repasscloud.com}

\section{Information We Collect}

We collect information from:

\begin{itemize}
\item You (when you create an account, use the Services, or contact support)
\item Your organisation (when they provision your access)
\item Your device and browser
\item Service providers that help us operate the Services
\end{itemize}

\subsection{Identity and Account Data}

\begin{itemize}
\item Name
\item Email address
\item Organisation name and identifiers
\item User identifiers and role assignments
\item Authentication identifiers issued by identity providers
\end{itemize}

\subsection{Authentication and Access Data}

We support enterprise authentication via Microsoft Entra ID (Azure AD) and may support federated identity providers.

We may process:

\begin{itemize}
\item Sign-in events and timestamps
\item Authentication logs
\item Access tokens and session identifiers
\item Multi-factor authentication status
\end{itemize}

\subsection{Customer Content and Business Data}

For enterprise SaaS platforms such as Cinturon360, customers may submit content that can include personal information, including:

\begin{itemize}
\item Traveller or employee profile details
\item Business contact details
\item Booking or operational data
\item Communications and support context
\end{itemize}

\subsection{Operational, Audit, and Security Logs}

We collect operational and security telemetry including:

\begin{itemize}
\item IP addresses
\item Authentication logs
\item Application and API access logs
\item Audit logs
\item Error logs and diagnostic traces
\item Performance telemetry
\end{itemize}

Retention policy:

\begin{itemize}
\item Minimum retention: 90 days
\item Typical deletion: after 100 days
\end{itemize}

\subsection{Device and Technical Data}

\begin{itemize}
\item Browser type and version
\item Device type and operating system
\item Approximate location derived from IP
\item Session metadata and performance metrics
\end{itemize}

\subsection{Billing and Payment Data}

If you purchase Services we process billing contact details and transaction metadata.

Payment processing may be handled by third-party providers such as Stripe. We do not store full payment card numbers.

\subsection{Support and Communications}

If you contact us we may collect:

\begin{itemize}
\item Support request content
\item Contact details
\item Diagnostics required to resolve issues
\item Records of communications
\end{itemize}

\section{How We Use Information}

We use personal information to:

\begin{itemize}
\item Provide and operate the Services
\item Authenticate users and manage access control
\item Deliver support and troubleshooting
\item Maintain security and detect fraud
\item Monitor reliability and performance
\item Comply with legal obligations
\item Handle billing and administration
\item Send marketing communications where permitted
\item Improve and market our services
\end{itemize}

We do not sell personal information.

\section{Legal Bases for Processing}

Where required by law (for example GDPR), we rely on one or more of:

\begin{itemize}
\item Contract
\item Legitimate interests
\item Consent
\item Legal obligation
\item Vital interests
\end{itemize}

\section{Hosting, Data Residency, and Infrastructure}

Customer data may be hosted in different regions depending on configuration and commercial terms.

Current and planned regions include:

\begin{itemize}
\item Australia (Microsoft Azure)
\item United States (AWS)
\item European Union (Hetzner EU)
\end{itemize}

\section{Cookies and Similar Technologies}

We use cookies and similar technologies for:

\begin{itemize}
\item Authentication
\item Security controls
\item Preferences and settings
\item Performance and reliability
\item Analytics and marketing
\end{itemize}

We partner with Microsoft Clarity and Microsoft Advertising to analyse website usage and improve services.

\section{Disclosure of Information}

We disclose personal information only as necessary to operate the Services, including to:

\begin{itemize}
\item Cloud hosting providers
\item Identity providers
\item Payment processors
\item Security vendors
\item Analytics and marketing vendors
\item Professional advisers
\item Authorities when legally required
\item Business transferees during mergers or acquisitions
\end{itemize}

\section{Security}

We maintain an information security program including:

\begin{itemize}
\item Encryption in transit and at rest
\item Role-based access control
\item Multi-factor authentication
\item Audit logging and monitoring
\item Secure development practices
\item Vulnerability management
\end{itemize}

No system is completely secure and we continuously improve safeguards.

\section{Data Retention}

We retain personal information only as long as necessary for the purposes described in this policy.

\begin{itemize}
\item Security logs retained approximately 90--100 days
\item Customer content retained according to customer contracts
\end{itemize}

\section{Data Breach Notification}

If a data breach occurs we will:

\begin{itemize}
\item Investigate and contain the incident
\item Notify affected customers when required
\item Provide information needed for regulatory obligations
\end{itemize}

\section{Your Rights}

Depending on jurisdiction you may have rights to:

\begin{itemize}
\item Access
\item Correction
\item Deletion
\item Restriction
\item Objection
\item Data portability
\item Withdraw consent
\end{itemize}

\section{Children's Privacy}

Our Services are not intended for children under 18 and we do not knowingly collect personal information from children.

\section{Changes to This Privacy Policy}

We may update this policy from time to time. The last updated date indicates when the policy was revised.

\section{Contact}

RePass Cloud Pty Ltd \\
PO BOX 262 \\
Bondi Junction NSW 1355 \\
Australia

Email: \href{mailto:hello@repasscloud.com}{hello@repasscloud.com}

\end{document}