\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{sourcesanspro}
\usepackage{array}
\usepackage{longtable}

\renewcommand{\familydefault}{\sfdefault}

\hyphenpenalty=500
\exhyphenpenalty=500
\emergencystretch=2em

\titleformat{\section}{\large\bfseries}{\thesection.}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{0.5em}{}

\setlist[itemize]{noitemsep,topsep=3pt}

\begin{document}

{\LARGE \textbf{Applicant Privacy Notice}}

\vspace{4pt}
RePass Cloud Pty Ltd

\vspace{2pt}
Effective: 2025-01-01

\vspace{12pt}

\section{Who We Are}

RePass Cloud Pty Ltd ("RePass Cloud", "we", "us") is an Australian-registered company headquartered in Sydney, New South Wales. This notice explains how we collect, use, store, and manage personal information during the hiring process.

We are bound by the \textit{Privacy Act 1988 (Cth)} and the Australian Privacy Principles (APPs).

\section{What Information We Collect}

During the hiring process, we may collect:

\begin{itemize}
\item Contact details (name, email address, phone number, location)
\item Resume or CV, portfolio links, and GitHub profile
\item Responses to application questions
\item Introduction video (if submitted)
\item Interview notes and assessments
\item Interview recordings (where applicable and consented to)
\item Reference check information (where conducted)
\end{itemize}

\section{How We Use Your Information}

We use applicant information solely for the purpose of evaluating your suitability for the role applied for. This includes:

\begin{itemize}
\item Reviewing your application and supporting materials
\item Conducting screening calls, technical interviews, and final interviews
\item Performing reference or background checks where required
\item Making and communicating hiring decisions
\end{itemize}

We do not sell, share, or use applicant data for marketing purposes. We do not reuse applicant data for future roles without your explicit consent.

\section{Interview Recordings}

Where interviews are recorded, you will be informed and asked to consent before any recording begins.

\begin{itemize}
\item \textbf{Unsuccessful applicants:} all recordings are deleted upon notification of the outcome. A confirmation email is sent to you.
\item \textbf{Successful applicants:} a written summary of your interview is retained as part of your employee record. The video recording is deleted upon execution of your employment or contractor agreement.
\end{itemize}

\section{Sharing Your Information}

In limited circumstances, we may share applicant information with third parties:

\begin{itemize}
\item \textbf{With clients}, where a consulting engagement requires it and where you have given explicit written consent at the technical or final interview stage. Without your consent, we cannot proceed with the application --- it will be marked as declined and all data deleted in accordance with this notice.
\item \textbf{With service providers} who assist us in running our recruitment process (e.g. background check providers), under appropriate confidentiality obligations.
\end{itemize}

\section{Data Retention}

\begin{longtable}{|>{\raggedright\arraybackslash}p{0.34\textwidth}|>{\raggedright\arraybackslash}p{0.58\textwidth}|}
\hline
\textbf{Applicant Status} & \textbf{Retention} \\
\hline
Unsuccessful applicant & Deleted upon notification of outcome \\
\hline
Active employee (first 90 days) & Relevant application data carried into employee record; non-required data removed after 90 days \\
\hline
Employee departed within 90 days & Application data removed promptly \\
\hline
Former employee & Minimum data retained only as required by Australian statutory obligations (e.g. Fair Work Act, taxation) \\
\hline
\end{longtable}

\section{Data Storage}

All applicant data is stored in Australia. We take reasonable technical and organisational measures to protect personal information against unauthorised access, loss, or misuse.

\section{Your Rights}

Under the \textit{Privacy Act 1988 (Cth)}, you have the right to:

\begin{itemize}
\item Request access to the personal information we hold about you
\item Request correction of inaccurate or incomplete information
\item Make a complaint if you believe your privacy rights have been breached
\end{itemize}

To exercise any of these rights, contact us via our \href{https://repasscloud.com/contact/}{contact page}.

\section{Agreement to This Notice}

By submitting an application, you confirm that you have read and agree to this Applicant Privacy Notice. Acceptance is required to submit an application via the RePass Cloud careers portal.

\section{Contact \& Complaints}

\textbf{RePass Cloud Pty Ltd} \\
Sydney, New South Wales, Australia \\
\href{https://repasscloud.com/contact/}{Contact page}

If you are not satisfied with our response to a privacy concern, you may contact the Office of the Australian Information Commissioner (OAIC) at \href{https://www.oaic.gov.au}{oaic.gov.au}.

\textit{This notice is subject to periodic review. The current version is published on our \href{https://repasscloud.com/careers/privacy/}{careers privacy page}.}
\end{document}