\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{sourcesanspro}

\renewcommand{\familydefault}{\sfdefault}

\sloppy

\titleformat{\section}{\large\bfseries}{\thesection.}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{0.5em}{}

\setlist[itemize]{noitemsep,topsep=3pt}

\begin{document}

{\LARGE \textbf{Privacy Policy}}

\vspace{4pt}
RePass Cloud Pty Ltd

\vspace{2pt}
Last updated: 2026-03-09

\vspace{12pt}

\section{Who We Are}

This Privacy Policy applies to RePass Cloud Pty Ltd ("RePass Cloud", "we", "us", or "our"). It explains how we collect, use, disclose, store, and protect personal information when you interact with our websites, products, and services (the "Services").

Our actively developed and maintained enterprise SaaS product is Cinturon360. We may also operate additional websites, brands, prototypes, or legacy products. This policy applies to all Services we operate that link to this Privacy Policy.

Examples of sites and brands that may link to this Privacy Policy include:

\begin{itemize}
\item \url{https://repasscloud.com}
\item Other RePass Cloud websites and service endpoints that link to this policy
\end{itemize}

Legacy services notice: Some legacy or discontinued projects may still reference RePass Cloud. Where a service is no longer operated by us, this Privacy Policy does not apply to any independent third-party forks, deployments, or uses of that software.

If you do not agree with this policy, do not use the Services.

\section{Roles: Controller and Processor}

Depending on the context, RePass Cloud may act as:

\begin{itemize}
\item \textbf{Data controller} -- for example, for account administration, billing, and operating our websites and marketing activities.
\item \textbf{Data processor / service provider} -- for example, when we process data on behalf of a business customer in enterprise SaaS products such as Cinturon360.
\end{itemize}

Business customers are typically the controller for customer content they upload to enterprise SaaS products. RePass Cloud processes that content to provide the Services under customer instructions, applicable agreements, and applicable law.

\section{Contact Details}

RePass Cloud Pty Ltd \\
PO BOX 262 \\
Bondi Junction NSW 1355 \\
Australia

Contact: \href{/contact}{contact page}

If you are a customer administrator and need to raise a security or privacy issue urgently, email \href{/contact}{contact page} and include "Privacy" or "Security" in the subject.

\section{Information We Collect}

We collect information from:

\begin{itemize}
\item You (when you create an account, use the Services, or contact support).
\item Your organisation (when they provision your access).
\item Your device and browser (when you access our websites and applications).
\item Service providers that help us operate the Services.
\end{itemize}

We collect the following categories of personal information, depending on how you use the Services.

\subsection{Identity and Account Data}

\begin{itemize}
\item Name
\item Email address
\item Organisation name and identifiers
\item User identifiers and role assignments
\item Authentication identifiers issued by identity providers
\end{itemize}

\subsection{Authentication and Access Data}

We support enterprise authentication via Microsoft Entra ID (Azure AD) and may support federated identity providers or OAuth sign-in options where customers require them. Password-based authentication may be enabled on a per-user basis.

We may process:

\begin{itemize}
\item Sign-in events and timestamps
\item Authentication logs
\item Access tokens and session identifiers (stored as needed for security)
\item Multi-factor authentication status (where supplied by identity provider)
\end{itemize}

Internal access for RePass Cloud personnel is restricted and uses Microsoft Entra ID authentication.

\subsection{Customer Content and Business Data (Enterprise SaaS)}

For enterprise SaaS (including Cinturon360), business customers may submit and store content that can include personal information, such as:

\begin{itemize}
\item Employee or user profile details
\item Business contact details
\item Operational data (where customers choose to use those features)
\item Communications and support context entered within the platform
\end{itemize}

This content is determined by the customer and their configuration and usage.

\subsection{Operational, Audit, and Security Logs}

We collect operational and security telemetry to protect the Services and meet audit requirements, including:

\begin{itemize}
\item IP addresses
\item Authentication logs
\item Application and API access logs
\item Audit logs (administrative actions and configuration changes)
\item Error logs and diagnostic traces
\item Performance and availability telemetry
\end{itemize}

Retention:

\begin{itemize}
\item We retain logs for a \textbf{minimum of 90 days}.
\item We delete logs after \textbf{100 days}, unless longer retention is required for contractual, legal, or security reasons (for example, an active investigation or legal hold).
\end{itemize}

We do not use logs for advertising purposes.

\subsection{Device and Technical Data}

\begin{itemize}
\item Browser type and version
\item Device type and operating system
\item Approximate location derived from IP (for security and fraud prevention)
\item Session metadata and performance metrics
\end{itemize}

\subsection{Billing and Payment Data}

If you purchase Services, we process billing contact details and transaction metadata. Payment processing may be handled by third-party payment providers such as Stripe. We do not store full payment card numbers.

\subsection{Support and Communications}

If you contact us, we may collect:

\begin{itemize}
\item The content of your request
\item Contact details
\item Diagnostics necessary to resolve your issue
\item Records of communications
\end{itemize}

\section{How We Use Information}

We use personal information for the following purposes:

\begin{itemize}
\item Provide and operate the Services, including user administration.
\item Authenticate users and manage sessions and access control.
\item Deliver support, troubleshoot issues, and respond to enquiries.
\item Maintain security, detect abuse, prevent fraud, and investigate incidents.
\item Monitor reliability and performance using internal telemetry and website analytics tools.
\item Comply with legal obligations and enforce our terms.
\item Business administration, including billing, accounting, and procurement.
\item Marketing communications where permitted by law and your preferences.
\item Improve and market our products and services using permitted analytics, behavioural metrics, and advertising technologies.
\end{itemize}

We do not sell personal information.

We do not use Google Analytics. We may use Microsoft Clarity and Microsoft Advertising as described in Section 8.

\section{Legal Bases for Processing}

Where applicable law requires a legal basis (for example under GDPR), we rely on one or more of the following:

\begin{itemize}
\item \textbf{Contract}: to provide the Services you or your organisation requested.
\item \textbf{Legitimate interests}: to secure and improve Services, prevent fraud, and protect our business and users.
\item \textbf{Consent}: where required for specific activities (for example certain marketing communications, analytics cookies, advertising cookies, or optional features).
\item \textbf{Legal obligation}: to comply with laws and respond to lawful requests.
\item \textbf{Vital interests}: to protect safety where applicable.
\end{itemize}

Where we act as a processor, the customer is responsible for determining the legal basis for customer content they provide to us.

\section{Hosting, Data Residency, and Infrastructure}

We host customer data using cloud infrastructure providers. Customers may choose hosting regions or providers depending on product configuration and commercial terms.

Current and planned hosting approach:

\begin{itemize}
\item Initial customers in Australia and New Zealand are hosted in \textbf{Microsoft Azure Australia} regions.
\item As we expand, we may host in other regions and providers to meet customer demand and data residency requirements, including:
  \begin{itemize}
  \item Australia (Azure)
  \item United States (AWS)
  \item European Union (Hetzner EU)
  \end{itemize}
\end{itemize}

If a customer is not explicitly configured for another region, hosting defaults to Australia.

\section{Cookies and Similar Technologies}

We use cookies and similar technologies primarily for:

\begin{itemize}
\item Authentication and session management
\item Security controls
\item Preferences and settings
\item Performance and reliability
\item Website analytics, optimisation, and, where permitted, advertising and marketing activities
\end{itemize}

We partner with Microsoft Clarity and Microsoft Advertising to capture how you use and interact with our website through behavioural metrics, heatmaps, and session replay to improve and market our products/services. Website usage data is captured using first and third-party cookies and other tracking technologies to determine the popularity of products/services and online activity. Additionally, we use this information for site optimisation, fraud/security purposes, and advertising. For more information about how Microsoft collects and uses your data, visit the \href{https://www.microsoft.com/privacy/privacystatement}{Microsoft Privacy Statement}.

You can control cookies through your browser settings. Some features may not work properly if you disable cookies. Where required by applicable law, we will request consent before using non-essential cookies or similar technologies.

We do not use Google Analytics or Google advertising cookies.

\section{Disclosure of Information}

We disclose personal information only as necessary to operate the Services, for the purposes described in this policy, and subject to appropriate protections.

We may disclose information to:

\begin{itemize}
\item Cloud infrastructure providers (for hosting and storage).
\item Identity providers (for authentication and access management).
\item Payment processors (for billing and payments).
\item Security and operational vendors (for monitoring and incident response).
\item Analytics, advertising, and marketing vendors used to improve, measure, and market our services, subject to applicable law.
\item Professional advisers (lawyers, auditors, insurers) under confidentiality.
\item Authorities where required by law or to protect rights and safety.
\item Business transferees in connection with a merger, acquisition, or sale.
\end{itemize}

We do not sell personal information.

\section{International Data Transfers}

We may process data in Australia, the United States, the European Union, or other jurisdictions depending on hosting configuration and service operations.

Where required, we implement safeguards such as:

\begin{itemize}
\item Contractual protections (including Standard Contractual Clauses where applicable)
\item Encryption and access controls
\item Vendor due diligence and security requirements
\end{itemize}

\section{Security}

We maintain an information security program designed to protect personal information. Controls may include:

\begin{itemize}
\item Encryption in transit (TLS) and encryption at rest
\item Role-based access control and least-privilege access
\item Multi-factor authentication and strong authentication requirements
\item Audit logging and monitoring
\item Segmentation and environment controls
\item Secure development and change management practices
\item Vulnerability management and incident response procedures
\end{itemize}

No method of transmission or storage is 100 percent secure. We continuously improve safeguards and respond to threats.

\section{Data Retention and Deletion}

We retain personal information only as long as necessary for the purposes described in this policy, including legal, tax, accounting, and security needs.

\begin{itemize}
\item Security and telemetry logs are generally retained for 90 to 100 days.
\item Customer content is retained according to customer instructions and contract terms.
\item Where deletion is requested, we will take reasonable steps to delete or de-identify data unless an exception applies (for example, legal hold, security investigation, or legal obligation).
\end{itemize}

Backups may retain data for limited periods, but data is isolated and protected and deleted in line with our backup lifecycle.

\section{Data Breach and Incident Notification}

If we become aware of a data breach affecting personal information, we will:

\begin{itemize}
\item Investigate and take steps to contain and remediate the incident.
\item Notify affected customers and users as required by applicable law and contract.
\item Provide information reasonably necessary for customers to meet their own legal obligations.
\end{itemize}

\section{Your Rights and Choices}

Your rights depend on where you live and how you use the Services.

\subsection{Australia and New Zealand}

We handle personal information under Australia's Privacy Act 1988 and the Australian Privacy Principles (APPs), and New Zealand's Privacy Act 2020.

You may request access to, or correction of, personal information we hold about you. You may also make a complaint.

\begin{itemize}
\item \textbf{Australia}: Office of the Australian Information Commissioner (OAIC) -- \href{https://www.oaic.gov.au}{oaic.gov.au}
\item \textbf{New Zealand}: Office of the Privacy Commissioner -- \href{https://www.privacy.org.nz}{privacy.org.nz}
\end{itemize}

\subsection{EEA, United Kingdom, and Switzerland}

Where GDPR or similar laws apply, you may have rights to:

\begin{itemize}
\item Access
\item Rectification
\item Erasure
\item Restriction
\item Objection
\item Data portability
\item Withdraw consent (where processing is based on consent)
\end{itemize}

You may also lodge a complaint with your local supervisory authority.

\subsection{United States State Privacy Laws}

Where applicable (for example California under CCPA/CPRA and other state laws), you may have rights to request access, correction, deletion, and to opt out of certain processing activities as defined by law.

We do not sell personal information.

Where applicable law treats certain analytics, cookie-based advertising, or similar disclosures as "sharing" or targeted advertising, you may have the right to opt out of that processing.

\section{Exercising Rights and Verification}

To request access, correction, deletion, or other rights, contact: \href{/contact}{contact page}

If you are using Services through an organisation, your administrator may need to submit certain requests. We may need to verify identity before fulfilling requests. We aim to respond within timeframes required by applicable law.

\section{Children's Privacy}

Our Services are not intended for children under 18 and we do not knowingly collect personal information from children.

\section{Changes to This Privacy Policy}

We may update this Privacy Policy from time to time. The "Last updated" date at the top indicates when this policy was most recently revised. Material changes may be communicated through the Services or by other appropriate means.

\section{Contact}

RePass Cloud Pty Ltd \\
PO BOX 262 \\
Bondi Junction NSW 1355 \\
Australia

Contact: \href{/contact}{contact page}

\end{document}
